Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/paper.tex
Minor fixes to the bibliography
Fix title in PDF metadata

\usepackage[usenames]{color}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

\bibitem{benton06reading}
N.~Benton, A.~Kennedy, M.~Hofmann, L.~Beringer.
Reading, Writing and Relations.
Proceedings, Asian Symposium on Programming Languages and Systems,
pp. 114-130, 2006

@@

\bibitem{harrison09without}
J.~Harrison.
Without Loss of Generality.
Proceedings, Theorem Proving in Higher Order Logics,
pp. 43-59, 2009

\bibitem{hofmann08correctness}
M. Hofmann. Correctness of effect-based program
transformations. Formal Logical Methods for System Security and
Correctness, pp. 149-173, 2008

\bibitem{jones95functional}
M. P. Jones.  Functional Programming with Overloading and Higher-Order
Polymorphism. Proceedings, Advanced Functional Programming,
pp. 97-136, 1995.

\bibitem{kennedy97relational} 
A. Kennedy. Relational Parametricity and Units of Measure.
Proceedings, Symposium on Principles of Programming Languages,
pp. 442-455, 1997.

@@

\bibitem{PittsAM:parpoe}
A. M. Pitts.  Parametric Polymorphism and Operational Equivalence.
{\em Mathematical Structures in Computer Science} 10, pp. 321-359,
2000.

\bibitem{reed10distance}
J. Reed and B. C. Pierce.  Distance Makes the Types Grow Stronger.
Proceeding, International Conference on Functional Programming,
pp. 157-169, 2010.

\bibitem{reynolds83types}
J. C. Reynolds. Types, Abstraction and Parametric Polymorphism.
{\em Information Processing} 83, pp. 513-523, 1983.

\bibitem{sabelfeld01per} 
A. Sabelfeld and D. Sands.  A Per Model of Secure Information Flow in
Sequential Programs.  {\em Higher-Order and Symbolic Computation} 14
(1), pp. 59-91, 2001.

\bibitem{tse04translating}
S. Tse and S. Zdancewic.  Translating Dependency into Parametricity.
Proceedings, International Conference on Functional Programming pp.
115-125, 2004.

\bibitem{wadler89theorems}
P. Wadler.  Theorems for Free!.  Proceedings, International Conference
on Functional Programming Languages and Computer Architecture,
pp. 347-359, 1989.

>>>>

\usepackage[usenames]{color}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Abstraction and Invariance for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}

@@

\bibitem{benton06reading}
N.~Benton, A.~Kennedy, M.~Hofmann, L.~Beringer.
Reading, Writing and Relations.
Proceedings, Asian Symposium on Programming Languages and Systems,
pp. 114-130, 2006.

@@

\bibitem{harrison09without}
J.~Harrison.
Without Loss of Generality.
Proceedings, Theorem Proving in Higher Order Logics,
pp. 43-59, 2009.

\bibitem{hofmann08correctness}
M.~Hofmann. Correctness of effect-based program
transformations. Formal Logical Methods for System Security and
Correctness, pp. 149-173, 2008.

\bibitem{jones95functional}
M.~P.~Jones.  Functional Programming with Overloading and Higher-Order
Polymorphism. Proceedings, Advanced Functional Programming,
pp. 97-136, 1995.

\bibitem{kennedy97relational} 
A.~Kennedy. Relational Parametricity and Units of Measure.
Proceedings, Symposium on Principles of Programming Languages,
pp. 442-455, 1997.

@@

\bibitem{PittsAM:parpoe}
A.~M.~Pitts.  Parametric Polymorphism and Operational Equivalence.
{\em Mathematical Structures in Computer Science} 10, pp. 321-359,
2000.

\bibitem{reed10distance}
J.~Reed and B.~C.~Pierce.  Distance Makes the Types Grow Stronger.
Proceeding, International Conference on Functional Programming,
pp. 157-169, 2010.

\bibitem{reynolds83types}
J.~C.~Reynolds. Types, Abstraction and Parametric Polymorphism.
{\em Information Processing} 83, pp. 513-523, 1983.

\bibitem{sabelfeld01per} 
A.~Sabelfeld and D.~Sands.  A Per Model of Secure Information Flow in
Sequential Programs.  {\em Higher-Order and Symbolic Computation} 14
(1), pp. 59-91, 2001.

\bibitem{tse04translating}
S.~Tse and S.~Zdancewic.  Translating Dependency into Parametricity.
Proceedings, International Conference on Functional Programming pp.
115-125, 2004.

\bibitem{wadler89theorems}
P.~Wadler.  Theorems for Free!.  Proceedings, International Conference
on Functional Programming Languages and Computer Architecture,
pp. 347-359, 1989.
